Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-06 tex/sections/apm.tex
Fix an error
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Interestingly, this approach can reduce the number of computation steps as well. When we use a hash calculator circuit
instead of the component, $out$ will be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by our component's circuit.
%
%\begin{tikzpicture}
%    \draw (0,0) -- (4,0) -- (4,4) -- (0,4) -- (0,0);
%\end{tikzpicture}

>>>>

Interestingly, this approach can also reduce the number of computation steps. When we use a hash calculator circuit
instead of our component, $out$ will be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.
%
%\begin{tikzpicture}
%    \draw (0,0) -- (4,0) -- (4,4) -- (0,4) -- (0,0);
%\end{tikzpicture}
